BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2016-12-31 Paper2/BOAST.tex
Minor corrections.

There are many different loop optimization techniques~\cite{wolf1991loop}. We
can cite loop skewing~\cite{wolfe1986loops} (derives nested loops wavefronts)
or loop interchange~\cite{allen1984automatic} (loop variables change places).

\FD{BV}{Bizarre la suite ici. Ca fait plus ``previous work''}
The importance of  correct loop imbrication on BLAS~\cite{lawson1979basic}
operations is studied in~\cite{soliman2009performance}, and shows performance
increase of a factor up to 5 when using correct loop imbrication. The
importance of code transformation is stressed in~\cite{ye2011porting}, where a
selection of GPU kernels are ported to CPU and optimized.

BOAST kernel description language should be able to express all these
optimizations. This gives us a set of constraints to implement in the language:
\begin{itemize}
\item Arbitrary number of variables have to be created and manipulated (types,
attributes, \ldots).
\item Procedures have to be abstracted (reunite Fortran and C like languages,
attributes, \ldots).
\item Functions must be available.
\item Variables, constants and functions should be able to be composed in
complex expressions.
\item Basic control structures (for, while, if/else, , \ldots) have to be abstracted.
\item Powerful array management features (allowing several dimensions, transformations,
indexing, \ldots).
\end{itemize}

@@

%%% MULTI-TARGET LANGUAGE GENERATION %%%
\subsubsection{Multi-target Language Generation\label{sec:multitarget}}
Language availability and performance varies between platforms. It is thus
important to express computing kernels in different languages, based on the
availability and their respective merits on the target platform. Some languages
have additional features, such as languages that target GPUs (OpenCL, CUDA), or
languages that support \FD{BV}{multi-threading?} threading paradigms (OpenMP). The developer should be
given tools to determine what kind of language is currently used in order to be
able to use those additional features.

>>>>

There are many different loop optimization techniques~\cite{wolf1991loop}. We
can cite loop skewing~\cite{wolfe1986loops} (derives nested loops wavefronts)
or loop interchange~\cite{allen1984automatic} (loop variables change places).
The importance of  correct loop imbrication on BLAS~\cite{lawson1979basic} %\FD{BV}{Bizarre la suite ici. Ca fait plus ``previous work''}
operations is studied in~\cite{soliman2009performance}, and shows performance
increase of a factor up to 5 when using correct loop imbrication. The
importance of code transformation is stressed in~\cite{ye2011porting}, where a
selection of GPU kernels are ported to CPU and optimized.

BOAST kernel description language should be able to express all these
optimizations. This gives us a set of constraints to implement in the language:
\begin{itemize}
\item Arbitrary number of variables have to be created and manipulated (types,
attributes, \ldots).
\item Procedures have to be abstracted (reunite Fortran and C like languages,
attributes, \ldots).
\item Functions must be available.
\item Variables, constants and functions should be able to be composed in
complex expressions.
\item Basic control structures (for, while, if/else, \ldots) have to be abstracted.
\item Powerful array management features (allowing several dimensions, transformations,
indexing, \ldots).
\end{itemize}

@@

%%% MULTI-TARGET LANGUAGE GENERATION %%%
\subsubsection{Multi-target Language Generation\label{sec:multitarget}}
Language availability and performance varies between platforms. It is thus
important to express computing kernels in different languages, based on the
availability and their respective merits on the target platform. Some languages
have additional features, such as languages that target GPUs (OpenCL, CUDA), or
languages that support multi-threading paradigms (OpenMP). The developer should be
given tools to determine what kind of language is currently used in order to be
able to use those additional features.
